Calendar-based graphics for visualising people's daily schedules

### 2017-07-18 main.Rmd
rewrite scales section

Section \ref{sec:algorithm} discusses the implementation applied to the fixed scale which is using the whole range of all the data values. The \code{scale} argument controls the scaling of the display. In addition to the fixed scale (\code{fixed}), the remaining options include free scale on all the days (\code{free}), day of the week only (\code{free_wday}), and day of the month only (\code{free_mday}) for different comparisons and emphases.

Grouping the cells according to the common period gives rise to these scales. The minimums and maximums obtained for every $(i, j)$ and $(m, n)$ allow for individual scale over all the single days. Similarly, $j$ indexing day of the week is grouped to determine the scales on days of a week, and $g$ representing the day in the month is for the scales on days of a month.

Figure \ref{fig:flinders-2016} is drawn on the fixed scale so that it makes the magnitudes comparable over the whole period of time. On the other hand, some sub-series of small magnitudes yet worth-noting behaviours may become invisible whilst embedded in the overall picture. These sorts of scales, as a result, complements the calendar-based visualisation in general. Figure \ref{fig:flinders-free} provides an example of the free scale on all the days.

@@

The abbreviated month labels located on the top left are obtained through $(\min{(x)}, \max{(y)})$ for every $(m, n)$. The weekday texts with a single letter are uniformly placed on the bottom of the whole canvas, that is $\min{(y)}$, with the central position of a cell $x / 2$ for each $j$.

>>>>

Section \ref{sec:algorithm} discusses the implementation applied to the fixed scale which is using the whole range of all the data values. The \code{scale} argument controls the scaling of the display. The fixed scale (\code{fixed}) is the default, meaning the data values in all positions to be scaled. The remaining options include free scale within each cell (\code{free}), cells derived from the same day of the week (\code{free_wday}), or cells from the same day of the month (\code{free_mday}). It utilises the comparisons of absolute or relative values, and the emphases of various types of variations.

Grouping the cells based on the same time period gives rise to the different scales. For example, the minimums and maximums obtained from each cell, that is every day $(i, j)$ together with $(m, n)$, result in local scale. The overall variation gives way to the individual shape. Figure \ref{fig:flinders-free} is an example of plotting line charts scaled locally. The daily variation is made more distinctive, compared to Figure \ref{fig:flinders-2016}.

Similarly, the same $j$ indexing day of the week is grouped to compute the scales in days of a week; in other words, the same value within a given $j$ corresponds to the same position across each $j$\textsuperscript{th} cell. To construct the scales for days of the month, $g$ representing day of the month is used. This makes it easier to compare shape of a given day across each month block. The scaling option combined with the calendar layouts offers a number of varieties to construct the plot.

@@

The abbreviated month labels located on the top left are obtained through $(\min{(x)}, \max{(y)})$ for every $(m, n)$. The weekday texts with a single letter are uniformly positioned on the bottom of the whole canvas, that is $\min{(y)}$, with the central position of a cell $x / 2$ for each $j$.

### 2017-07-18 main.tex
rewrite scales section

Section \ref{sec:algorithm} discusses the implementation applied to the
fixed scale which is using the whole range of all the data values. The
\code{scale} argument controls the scaling of the display. In addition
to the fixed scale (\code{fixed}), the remaining options include free
scale on all the days (\code{free}), day of the week only
(\code{free_wday}), and day of the month only (\code{free_mday}) for
different comparisons and emphases.

Grouping the cells according to the common period gives rise to these
scales. The minimums and maximums obtained for every \((i, j)\) and
\((m, n)\) allow for individual scale over all the single days.
Similarly, \(j\) indexing day of the week is grouped to determine the
scales on days of a week, and \(g\) representing the day in the month is
for the scales on days of a month.

Figure \ref{fig:flinders-2016} is drawn on the fixed scale so that it
makes the magnitudes comparable over the whole period of time. On the
other hand, some sub-series of small magnitudes yet worth-noting
behaviours may become invisible whilst embedded in the overall picture.
These sorts of scales, as a result, complements the calendar-based
visualisation in general. Figure \ref{fig:flinders-free} provides an
example of the free scale on all the days.

@@

The abbreviated month labels located on the top left are obtained
through \((\min{(x)}, \max{(y)})\) for every \((m, n)\). The weekday
texts with a single letter are uniformly placed on the bottom of the
whole canvas, that is \(\min{(y)}\), with the central position of a cell
\(x / 2\) for each \(j\).

>>>>

Section \ref{sec:algorithm} discusses the implementation applied to the
fixed scale which is using the whole range of all the data values. The
\code{scale} argument controls the scaling of the display. The fixed
scale (\code{fixed}) is the default, meaning the data values in all
positions to be scaled. The remaining options include free scale within
each cell (\code{free}), cells derived from the same day of the week
(\code{free_wday}), or cells from the same day of the month
(\code{free_mday}). It utilises the comparisons of absolute or relative
values, and the emphases of various types of variations.

Grouping the cells based on the same time period gives rise to the
different scales. For example, the minimums and maximums obtained from
each cell, that is every day \((i, j)\) together with \((m, n)\), result
in local scale. The overall variation gives way to the individual shape.
Figure \ref{fig:flinders-free} is an example of plotting line charts
scaled locally. The daily variation is made more distinctive, compared
to Figure \ref{fig:flinders-2016}.

Similarly, the same \(j\) indexing day of the week is grouped to compute
the scales in days of a week; in other words, the same value within a
given \(j\) corresponds to the same position across each
\(j\)\textsuperscript{th} cell. To construct the scales for days of the
month, \(g\) representing day of the month is used. This makes it easier
to compare shape of a given day across each month block. The scaling
option combined with the calendar layouts offers a number of varieties
to construct the plot.

@@

The abbreviated month labels located on the top left are obtained
through \((\min{(x)}, \max{(y)})\) for every \((m, n)\). The weekday
texts with a single letter are uniformly positioned on the bottom of the
whole canvas, that is \(\min{(y)}\), with the central position of a cell
\(x / 2\) for each \(j\).
